Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-11-25 manuscript.Rmd
added acs demographic data and script to get it

load("data/travel_times.RData")
theme_map <- theme_void()

travel_times <- travel_times %>%
	mutate(origin_id = factor(origin_id),
				 dest_id = factor(dest_id))

@@

```{r join_sf}
dc_census <- st_read("data/uber_dc_tracts.json") %>%
	select("id" = MOVEMENT_ID, geometry) %>%
	mutate(id = factor(id, levels = levels(travel_times$dest_id)))

travel_time_sf <- left_join(x = travel_times, y = dc_census, by = c("dest_id" = "id")) %>%
	st_as_sf() %>%
	st_transform(crs = 102285)
```

```{r map}
travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	theme_map +
	scale_fill_viridis_c(direction = -1)

@@

>>>>

load("data/travel_times_census_join.RData")
load("data/dc_acs_tracts.RData")
theme_map <- theme_void()

# Could also directly import census demographic data using tidycensus package
demographic_data <- read.csv("data/DC_demographic_data.csv", header = FALSE)
names <- unlist(demographic_data[2,])
demographic_data <- demographic_data %>% 
  slice(3:8096)
head(demographic_data)
colnames(demographic_data) <- names
head(demographic_data)

@@

```{r join_sf}
travel_time_sf <- left_join(x = travel_times_census_join, y = dc_acs_tracts, by = "GEOID") %>%
	st_as_sf() %>%
	st_transform(crs = 102285)
```

```{r map_travel_timne}
travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	theme_map +
	scale_fill_viridis_c(direction = -1)

@@

```{r map_acs}
travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = med_incomeE)) +
	theme_map +
	scale_fill_viridis_c()
```
